Contrast Set Learning using WHAT

### 2015-04-05 manuscript.tex
Manuscripy

\section{Introduction}
\section{Background}
\section{Experimental Design}
\subsection{The Planning Algorithm}

\section{Experimental Results}
\section{Discussion}
\section{Threats to validity}
\section{Conclusion}
\section*{Acknowledgements}
\begin{thebibliography}{10}
\bibitem{test}
\end{thebibliography}
\end{document}

>>>>

\section{Introduction}
\section{Background}
\subsection{The Planning Algorithm}
The planning scheme makes use of WHERE to recursively split the data into smaller clusters. Following this, a nearest neighbour scheme is applied to identify pairs of nearby clusters. A projective plane is constructed with these clusters at the vertices to characterize the cluster pairs.

The mutation policy works by projecting the test instance onto the projective planes and identifying the the plane on which the test instance has the largest scalar projection. WHAT reflects over the vertices of the chosen hyperplane,  identifying the \textit{better} vertex among the two. A new instance is generated by mutating the attributes of the test instance towards the better vertex and away from the worse vertex. This process is repeated for all the test instance that are considered defective.
\section{Experimental Design}

\section{Experimental Results}
\section{Discussion}
\section{Threats to validity}
\section{Conclusion}
\section*{Acknowledgements}
%\begin{thebibliography}{10}
%\bibitem{test}
%\end{thebibliography}
\end{document}
